High-Dimensional Regularized Discriminant Analysis

### 2016-01-01 reports/paper-hdrda.Rnw
Added plot of sim error rates to paper

opts_chunk$set(fig.align = 'default', dev = 'png', message = FALSE,
               warning = FALSE, cache = TRUE, echo = FALSE, autodep = TRUE,
               fig.width = 12, fig.height = 12, out.width = "\\linewidth")
@

@@

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.33\\linewidth', fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 0.2)
rda_contours(lambda = 0.4)
rda_contours(lambda = 0.6)
rda_contours(lambda = 0.8)
rda_contours(lambda = 1)
@
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\subsubsection{Results}

@@

Regardless of the value of $rho$, $p$, or $\bm \mu$, random forests consistently
yielded the highest average error rate, and the average error rate for random
forests was much more pronounced when $\bm \mu=0.5$. However, as the
contaminated probability increased, random forests became increasingly
competitive, and, in some cases, e.g, $\bm \mu=0.5$, $p=100$, and contaminated
probability greater than 0.05 yielded the lowest average error rate.

>>>>

opts_chunk$set(fig.align='default', dev='png', message=FALSE, warning=FALSE,
               cache=TRUE, echo=FALSE, autodep=TRUE, fig.width=12,
               fig.height=12, out.width="\\linewidth")
@

@@

# Contaminated Normal Sims
results_contaminated <- lapply(results_block_contaminated[[1]], function(r) {
  with(r, c(error_rates, p=p, mu=mu, contamination_prob=contamination_prob))
})
results_contaminated <- do.call(rbind.data.frame, results_contaminated)
results_contaminated <- tbl_df(results_contaminated)

results_contaminated <- results_contaminated %>%
  group_by(p, contamination_prob, mu) %>%
  summarise_each(funs(mean)) %>%
  arrange(p, contamination_prob, mu)

results_contaminated <- results_contaminated %>%
  gather(Classifier, Error, -p, -contamination_prob, -mu) %>%
  mutate(p=factor(p)) %>%
  filter(mu == 0.5)

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.33\\linewidth', dpi=200, fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 0.2)
rda_contours(lambda = 0.4)
rda_contours(lambda = 0.6)
rda_contours(lambda = 0.8)
rda_contours(lambda = 1)
@
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\subsubsection{Simulation Results}

@@

\begin{figure}
<<sim_results, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(results_contaminated, aes(x=contamination_prob, y=Error))
p <- p + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p <- p + facet_wrap(~ p, labeller = "label_both")
p <- p + xlab("Contamination Probability") + ylab("Error Rate")
p + theme_bw()
@
\caption{Averages of the 1000 error-rate estimates of the competing classifiers
  for each data set as a function of $d$. Approximate standard errors are no
  greater than \Sexpr{max_se}.}
\label{fig:sim-results}
\end{figure}
Regardless of the value of $rho$, $p$, or $\bm \mu$, random forests consistently
yielded the highest average error rate, and the average error rate for random
forests was much more pronounced when $\bm \mu=0.5$. However, as the
contaminated probability increased, random forests became increasingly
competitive, and, in some cases, e.g, $\bm \mu=0.5$, $p=100$, and contaminated
probability greater than 0.05 yielded the lowest average error rate.
